Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-25 analysis/paper/paper.Rnw
removed cached files in analysis/figures
removed calls to knitr::include_graphics()

We generated scatter plots of pleiotropy test statistics vs. mediation LOD difference values for each of the five hotspots (Figure~\ref{}, \ref{}).
Each point represents a pairing of a local trait with a nonlocal trait.
The mediation LOD difference value is that observed when the local trait is considered
as a candidate mediator of the QTL-nonlocal trait association.

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 2 hotspot.">>=
include_graphics(paste0("../figures/Chr", hot_chr, "_scatter.pdf"))
@

@@

<<panel1, fig.cap = paste0("Chr", hot_chr, "hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.")>>=
include_graphics(paste0("../figures/Chr", hot_chr, "_scatter-panel1.pdf"))
@

<<panel2, eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 1>>=
include_graphics(paste0("../figures/Chr", hot_chr, "_scatter-panel2.pdf"))
@

<<panel3, eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 2>>=
include_graphics(paste0("../figures/Chr", hot_chr, "_scatter-panel3.pdf"))
@

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 5 hotspot.">>=
include_graphics("../figures/Chr5_scatter.pdf")
@

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 7 hotspot.">>=
include_graphics("../figures/Chr7_scatter.pdf")
@

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 11 hotspot.">>=
include_graphics("../figures/Chr11_scatter.pdf")
@

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 13 hotspot.">>=
include_graphics("../figures/Chr13_scatter.pdf")
@

>>>>

We generated scatter plots of pleiotropy test statistics vs. mediation LOD difference values for each of the five hotspots (Figure).
Each point represents a pairing of a local trait with a nonlocal trait.
The mediation LOD difference value is that observed when the local trait is considered
as a candidate mediator of the QTL-nonlocal trait association.

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 2 hotspot.">>=
#include_graphics(paste0("../figures/Chr", hot_chr, "_scatter.pdf"))
@

@@

<<panel1, fig.cap = paste0("Chr", hot_chr, "hotspot scatter plots of mediation LOD difference against pleiotropy LOD, separated by local trait.")>>=
#include_graphics(paste0("../figures/Chr", hot_chr, "_scatter-panel1.pdf"))
@

<<panel2, eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 1>>=
#include_graphics(paste0("../figures/Chr", hot_chr, "_scatter-panel2.pdf"))
@

<<panel3, eval = nfig[which(names(nfig) == paste0("Chr", hot_chr))] > 2>>=
#include_graphics(paste0("../figures/Chr", hot_chr, "_scatter-panel3.pdf"))
@

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 5 hotspot.">>=
#include_graphics("../figures/Chr5_scatter.pdf")
@

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 7 hotspot.">>=
#include_graphics("../figures/Chr7_scatter.pdf")
@

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 11 hotspot.">>=
#include_graphics("../figures/Chr11_scatter.pdf")
@

@@

<<fig.cap="Scatter plot of mediation LOD difference against pleiotropy LOD for all nonlocal-local trait pairs mapping to Chromosome 13 hotspot.">>=
#include_graphics("../figures/Chr13_scatter.pdf")
@
